DATA 621 Homework #4

### 2019-11-08 hw4/HW4.Rmd
More work on HW4

hw4_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

  plot_2 <- ggplot(df, aes(X, TARGET_AMT, color = TARGET_FLAG)) +
    geom_point() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- as.factor(as.character(df[[var]]))
  }
  plot_1_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
  plot_1 <- df %>%
    group_by(X, TARGET_FLAG) %>%
    tally() %>%
    ggplot(.) +
    geom_bar(aes(X, n, fill = TARGET_FLAG), stat="identity") +
    scale_fill_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT, color = X)) +
      geom_boxplot() +
      scale_color_brewer(palette="Dark2") + #Paired
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

@@

```{r} 
hw4_plot(df, "BLUEBOOK", TRUE)
```

@@

```{r} 
hw4_plot(df, "HOME_VAL", TRUE)
```

@@

```{r} 
hw4_plot(df, "INCOME", TRUE)
```

@@

```{r} 
hw4_categorical_plot(df, "MVR_PTS")
hw4_target_table(df, "MVR_PTS")
```

@@

Looking at the data, we can see that there are some missing values:

>>>>

hw4_plot <- function(df, var, strip_dollar_signs = FALSE, x_log_scale = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  if(x_log_scale){
    df$X <- log10(df$X)
  }
  # plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
  #   geom_jitter() +
  #   scale_color_brewer(palette="Set1") +
  #   theme_minimal() +
  #   theme(legend.position = "none",
  #         axis.title.x = element_blank(),
  #         axis.title.y = element_blank())

@@

  plot_2 <- ggplot(df, aes(X, TARGET_AMT, color = TARGET_FLAG)) +
    geom_point() +
    scale_color_brewer(palette="Set1") +
    scale_y_log10(labels=comma) +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- as.factor(as.character(df[[var]]))
  }
  # plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
  #   geom_jitter() +
  #   scale_color_brewer(palette="Set1") +
  #   theme_minimal() +
  #   theme(legend.position = "none",
  #         axis.title.x = element_blank(),
  #         axis.title.y = element_blank())
  temp <- df %>%
    group_by(X, TARGET_FLAG) %>%
    tally()
  temp <- df %>%
    group_by(X) %>%
    tally() %>%
    rename(TOTAL = n) %>%
    merge(temp) %>%
    mutate(PERCENT = n / TOTAL)
  plot_1 <-  temp %>%
    ggplot(.) +
    geom_bar(aes(X, PERCENT, fill = TARGET_FLAG), stat="identity") +
    scale_fill_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT, color = X)) +
      geom_boxplot() +
      scale_y_log10() +
      scale_color_brewer(palette="Dark2") + #Paired
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

@@

```{r} 
hw4_plot(df, "BLUEBOOK", TRUE, TRUE)
```

@@

```{r} 
hw4_plot(df, "HOME_VAL", TRUE, TRUE)
```

@@

```{r} 
hw4_plot(df, "INCOME", TRUE, TRUE)
```

@@

```{r} 
hw4_plot(df, "MVR_PTS")
```

@@

### OLDCLAIM

**Theoretical Effect**
If your total payout over the past five years was high, you are more likely to get into crashes.

```{r} 
hw4_plot(df, "OLDCLAIM", TRUE, TRUE)
```

### PARENT1

```{r} 
hw4_categorical_plot(df, "PARENT1")
hw4_target_table(df, "PARENT1")
```

### RED_CAR

**Theoretical Effect**
Urban legend says that red cars (espcially red sports cars) are more risky. Is that true?

```{r} 
hw4_categorical_plot(df, "RED_CAR")
hw4_target_table(df, "RED_CAR")
```

### REVOKED

**Theoretical Effect**
If your license was revoked in the pat 7 years, you probably are a more risky driver.

```{r}
hw4_categorical_plot(df, "REVOKED")
hw4_target_table(df, "REVOKED")
```

### SEX

**Theoretical Effect**
Urban legend says that women have less crashes then men.  Is that true?

```{r}
hw4_categorical_plot(df, "SEX")
hw4_target_table(df, "SEX")
```

### TIF

**Theoretical Effect**
People who have been customers for a long time are usually more safe.

```{r}
hw4_plot(df, "TIF")
```

### TRAVTIME

**Theoretical Effect**
Log drives to work usually suggest greater risk

```{r}
hw4_plot(df, "TRAVTIME")
```

### URBANICITY

**Theoretical Effect**
Unknown

```{r}
hw4_categorical_plot(df, "URBANICITY")
hw4_target_table(df, "URBANICITY")
```

### YOJ

**Theoretical Effect**
People who stay at a job for a long time are usuaslly more safe

```{r}
hw4_plot(df, "YOJ")
```

**Observed Effect**
INSERT TEXT HERE
Looking at the data, we can see that there are some missing values:
